---
title: "Solomon Islands"
author: "Yingmai Chen"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE,include=FALSE}
library(shiny)
library(leaflet)
library(sf)
library(ggplot2)
library(DT)
library(jsonlite)
library(tidyverse)
library(plotly)
```

```{r echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
solomon_islands <- st_read("solomon islands.geojson")
```

```{r echo=FALSE,warning=FALSE}
ui <- fluidPage(
    titlePanel("Map and Information of the Solomon Islands"),
    
    leafletOutput("map"),

    fluidRow(
        column(4, wellPanel(
            h4("Location"),
            "Southwestern Pacific Ocean"
        )),
        column(4, wellPanel(
            h4("Major Islands"),
            "6 major and over 900 smaller islands"
        )),
        column(4, wellPanel(
            h4("Capital"),
            "Honiara, located on Guadalcanal"
        )),
        column(4, wellPanel(
            h4("Area"),
            "Approximately 29,000 square kilometers"
        ))
    )
)

server <- function(input, output) {
    output$map <- renderLeaflet({
        leaflet(data = solomon_islands) %>%
            addTiles() %>%
            addPolygons()
    })
}

shinyApp(ui = ui, server = server)

```

First,I create a map to show the geographical position of the solomon islands.I frame its position in blue and I also list some information below the image.data is from (<https://github.com/glynnbird/countriesgeojson/blob/master/solomon%20islands.geojson>)

```{r echo=FALSE}
# Your existing data
solomon_data <- data.frame(
  year = c(1568, 1886, 1893, 1942, 1978, 1998),
  event = c("First European contact by Alvaro de Mendana", 
            "British-German Agreement", 
            "British Protectorate established", 
            "World War II", 
            "Independence from UK", 
            "Ethnic tensions and civil war"),
  category = c("Exploration", "Colonialism", "Colonialism", "War", "Independence", "Conflict")
)

# UI
ui <- fluidPage(
    titlePanel("Key Facts About the Solomon Islands"),
    sidebarLayout(
        sidebarPanel(
            sliderInput("yearRange", 
                        "Select Year Range:",
                        min = 1550, 
                        max = 2020, 
                        value = c(1550, 2020),
                        step = 10)
        ),
        mainPanel(
           DTOutput("eventTable"),
           plotOutput("timelinePlot")
        )
    )
)

# Server
server <- function(input, output) {
    # For the table
    output$eventTable <- renderDT({  
        filtered_data <- solomon_data[solomon_data$year >= input$yearRange[1] & solomon_data$year <= input$yearRange[2], ]
        datatable(filtered_data, options = list(pageLength = 5))
    })

    # For the plot
    output$timelinePlot <- renderPlot({
        filtered_data <- solomon_data[solomon_data$year >= input$yearRange[1] & solomon_data$year <= input$yearRange[2], ]
     
        filtered_data$period <- cut(filtered_data$year,
                                    breaks = c(1550, 1886, 1978, 2020),
                                    labels = c("Arrival of Europeans", "Colonial Period", "Independence Era"),
                                    include.lowest = TRUE)

        ggplot(filtered_data, aes(x = year, y = category, label = event, color = period)) +
            geom_point(size = 4) +
            geom_text(vjust = 2, angle = 45, hjust = 1, size = 4) +
            scale_x_continuous(breaks = filtered_data$year) +
            scale_color_manual(values = c("red", "black", "blue")) +
            theme_minimal() +
            labs(title = "Key Events in Solomon Islands' History", x = "Year", y = "Category") +
            theme(axis.text.y = element_blank(),
                  plot.title = element_text(hjust = 0.5),
                  panel.background = element_rect(fill = "lightblue"),
                  panel.grid.major = element_line(color = "white"),
                  panel.grid.minor = element_line(color = "white"),
                  legend.position = "bottom")
    })
}

# Run the application
shinyApp(ui = ui, server = server)

```

Then I show some key features for the solomon islands.Data(<https://en.wikipedia.org/wiki/Solomon_Islands>)

Description:The Solomon Islands, located in the southwestern Pacific Ocean, is an archipelago nation comprising six major islands and over 900 smaller ones. It's part of Melanesia in Oceania, northeast of Australia. The islands have a rich history, first settled around 30,000 BC. They gained independence from the United Kingdom in 1978. The capital, Honiara, is on Guadalcanal, the largest island. The Solomon Islands are known for their diverse cultures, languages, and a vibrant ecosystem, including rainforests and coral reefs.

# Key demographics

```{r echo=FALSE}
solomon_islands_data <- data.frame(
  Number = 1:9,
  Province = c("Central Province", "Choiseul Province", "Guadalcanal Province", "Isabel Province", "Makira-Ulawa Province", "Malaita Province", "Rennell and Bellona Province", "Temotu Province", "Western Province"),
  Capital = c("Tulagi", "Taro Island", "Honiara", "Buala", "Kirakira", "Auki", "Tigoa", "Lata", "Gizo"),
  Premier = c("Stanely Manetiva", "Harrison Benjamin", "Anthony Veke", "Lesley Kikolo", "Julian Maka'a", "Martin Fini", "Japhet Tuhanuku", "Clay Forau", "David Gina"),
  Area = c(615, 3837, 5336, 4136, 3188, 4225, 671, 895, 5475),
  Population_1999 = c(21577, 20008, 60275, 20421, 31006, 122620, 2377, 18912, 62739),
  Population_per_km2_2009 = c(42.4, 6.9, 17.5, 6.3, 12.7, 32.6, 4.5, 23.9, 14.0),
  Population_2009 = c(26051, 26371, 93613, 26158, 40419, 137596, 3041, 21362, 76649),
  Population_2022 = c(33476, 38453, 166838, 36688, 57396, 163085, 4465, 25701, 102083)
)

ui <- fluidPage(
  DTOutput("solomon_table")
)

server <- function(input, output) {
  output$solomon_table <- renderDT({
    datatable(solomon_islands_data, options = list(
      autoWidth = TRUE,
      columnDefs = list(list(width = '200px', targets = "_all"))
    ))
  })
}

shinyApp(ui = ui, server = server)

```

```{r echo=FALSE,warning=FALSE}
solomon_islands_data <- data.frame(
  Number = 1:9,
  Province = c("Central Province", "Choiseul Province", "Guadalcanal Province", "Isabel Province", "Makira-Ulawa Province", "Malaita Province", "Rennell and Bellona Province", "Temotu Province", "Western Province"),
  Capital = c("Tulagi", "Taro Island", "Honiara", "Buala", "Kirakira", "Auki", "Tigoa", "Lata", "Gizo"),
  Premier = c("Stanely Manetiva", "Harrison Benjamin", "Anthony Veke", "Lesley Kikolo", "Julian Maka'a", "Martin Fini", "Japhet Tuhanuku", "Clay Forau", "David Gina"),
  Area = c(615, 3837, 5336, 4136, 3188, 4225, 671, 895, 5475),
  Population_1999 = c(21577, 20008, 60275, 20421, 31006, 122620, 2377, 18912, 62739),
  Population_per_km2_2009 = c(42.4, 6.9, 17.5, 6.3, 12.7, 32.6, 4.5, 23.9, 14.0),
  Population_2009 = c(26051, 26371, 93613, 26158, 40419, 137596, 3041, 21362, 76649),
  Population_2022 = c(33476, 38453, 166838, 36688, 57396, 163085, 4465, 25701, 102083)
)
ui <- fluidPage(
  titlePanel("Population of Solomon Islands Provinces"),
  selectInput("year", "Select Year", choices = c("1999", "2009", "2022")),
  plotOutput("populationPlot")
)


server <- function(input, output) {
  output$populationPlot <- renderPlot({
    year_col <- paste0("Population_", input$year)
    data_to_plot <- solomon_islands_data %>%
      select(Province, Population = all_of(year_col))
ggplot(data_to_plot, aes(x = Province, y = Population, fill = Province)) +
  geom_bar(stat = "identity", color = "black", size = 0.5) +  # Adds a border to the bars
  theme_minimal(base_size = 14) +  # Uses a minimal theme with larger base font size
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12, face = "bold"), # Bolder, larger x-axis labels
    axis.text.y = element_text(size = 12, face = "bold"), # Bolder y-axis labels
    axis.title = element_text(size =  14, face = "bold"), # Bolder axis titles
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5) # Bolder and centered plot title
  ) +
  labs(y = "Population", x = "Province", title = paste("Population of Solomon Islands Provinces in", input$year)) +
  scale_fill_brewer(palette = "Paired")  

  })
}

shinyApp(ui = ui, server = server)
```

We can see from the Solomon Islands that the population of key provinces has increased significantly in both periods, 1999-2009, 2009-2022.

```{r echo=FALSE}
data <- data.frame(
  Category = rep(c("Geography", "Culture", "History", "Economy", "Demographics"), each = 5),
  Island = c(rep(c("Solomon Islands", "Fiji", "Vanuatu", "Papua New Guinea", "New Caledonia"), 5)),
Information = c(
  # Geography
  "Six major islands and over 900 smaller ones, volcanic mountain ranges, dense rainforests, lagoons",
  "More than 330 islands, rugged landscapes, palm-lined beaches, coral reefs",
  "About 82 volcanic islands",
  "Eastern half of New Guinea, dense rainforests, active volcanoes",
  "French territory, numerous islands, palm-lined beaches, rich marine life",
  # Culture
  "Diverse ethnic groups, wood carvings, music, dance",
  "Multicultural, indigenous Fijian, Indo-Fijian, Pacific Islander cultures",
  "Strong Melanesian culture, land diving rituals",
  "Hundreds of ethnic groups and languages",
  "Mix of French and Melanesian cultures, Kanak traditions",
  # History
  "Influenced by European exploration, colonialism, and World War II",
  "Former British colony until 1970",
  "Anglo-French condominium until 1980",
  "Independent from Australia since 1975",
  "French territory, with ongoing independence discussions",
  # Economy
  "Based on agriculture, forestry, fishing, and mining",
  "Diversified economy with tourism, sugar, and garment industries",
  "Agricultural economy with significant tourism",
  "Rich in natural resources, with an economy centered on mining",
  "Large economy supported by nickel mining and French financial aid",
  # Demographics
  "Predominantly Melanesian, with Polynesian and Micronesian communities",
  "Majority indigenous Fijians and Indo-Fijians",
  "Primarily Ni-Vanuatu (Melanesian)",
  "Over 800 languages spoken",
  "Majority Kanak (indigenous Melanesians), with Europeans, Polynesians, and Southeast Asians"
)
)
ui <- fluidPage(
  titlePanel("Comparative Analysis of Melanesian Islands"),
  sidebarLayout(
    sidebarPanel(
      selectInput("category", "Select Category:", choices = c("Geography", "Culture", "History", "Economy", "Demographics"))
    ),
    mainPanel(
      tableOutput("infoTable")
    )
  )
)

# Define server logic
server <- function(input, output) {
  output$infoTable <- renderTable({
    # Filter data based on the selected category
    filteredData <- data %>% filter(Category == input$category)
    return(filteredData)
  })
}

# Run the application 
shinyApp(ui = ui, server = server)

```

# SWOT analysis
```{r}
ui <- fluidPage(
    titlePanel("Solomon Islands GDP Composition(2011)"),
    plotlyOutput("gdpPieChart")
)

# Define server logic to draw the pie chart
server <- function(input, output) {
    output$gdpPieChart <- renderPlotly({
        # Data for the pie chart
        sectors <- c("Agriculture", "Industry", "Services")
        percentages <- c(37.7, 6.4, 55.9)
        colors <- c('#FF9999', '#66B2FF', '#99CC99')  # Custom color palette

        # Create the pie chart
        plot_ly(labels = sectors, values = percentages, type = 'pie',
                textinfo = 'label+percent',
                insidetextorientation = 'radial', marker = list(colors = colors),
                hoverinfo = 'label+percent+name') %>%
            layout(
                   legend = list(x = 1, y = 0.5),
                   titlefont = list(size = 20))
    })
}

# Run the application
shinyApp(ui = ui, server = server)
```

