---
title: "Solomon Islands"
author: "Yingmai Chen"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE,include=FALSE}

library(shiny)
library(leaflet)
library(sf)
library(ggplot2)
library(DT)
library(jsonlite)
library(tidyverse)
library(plotly)
library(tidyr)
library(reshape2)
library(scales)
```

```{r echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
solomon_islands <- st_read("solomon islands.geojson")
```

```{r echo=FALSE,warning=FALSE}
ui <- fluidPage(
    titlePanel("Map and Information of the Solomon Islands"),
    
    leafletOutput("map"),

    fluidRow(
        column(4, wellPanel(
            h4("Location"),
            "Southwestern Pacific Ocean"
        )),
        column(4, wellPanel(
            h4("Major Islands"),
            "6 major and over 900 smaller islands"
        )),
        column(4, wellPanel(
            h4("Capital"),
            "Honiara, located on Guadalcanal"
        )),
        column(4, wellPanel(
            h4("Area"),
            "Approximately 29,000 square kilometers"
        ))
    )
)

server <- function(input, output) {
    output$map <- renderLeaflet({
        leaflet(data = solomon_islands) %>%
            addTiles() %>%
            addPolygons()
    })
}

shinyApp(ui = ui, server = server)

```

First,I create a map to show the geographical position of the solomon islands.I frame its position in blue and I also list some information below the image.data is from (<https://github.com/glynnbird/countriesgeojson/blob/master/solomon%20islands.geojson>)

```{r echo=FALSE}
# Your existing data
solomon_data <- data.frame(
  year = c(1568, 1886, 1893, 1942, 1978, 1998),
  event = c("First European contact by Alvaro de Mendana", 
            "British-German Agreement", 
            "British Protectorate established", 
            "World War II", 
            "Independence from UK", 
            "Ethnic tensions and civil war"),
  category = c("Exploration", "Colonialism", "Colonialism", "War", "Independence", "Conflict")
)

# UI
ui <- fluidPage(
    titlePanel("Key Facts About the Solomon Islands"),
    sidebarLayout(
        sidebarPanel(
            sliderInput("yearRange", 
                        "Select Year Range:",
                        min = 1550, 
                        max = 2020, 
                        value = c(1550, 2020),
                        step = 10)
        ),
        mainPanel(
           DTOutput("eventTable"),
           plotOutput("timelinePlot")
        )
    )
)

# Server
server <- function(input, output) {
    # For the table
    output$eventTable <- renderDT({  
        filtered_data <- solomon_data[solomon_data$year >= input$yearRange[1] & solomon_data$year <= input$yearRange[2], ]
        datatable(filtered_data, options = list(pageLength = 5))
    })

    # For the plot
    output$timelinePlot <- renderPlot({
        filtered_data <- solomon_data[solomon_data$year >= input$yearRange[1] & solomon_data$year <= input$yearRange[2], ]
     
        filtered_data$period <- cut(filtered_data$year,
                                    breaks = c(1550, 1886, 1978, 2020),
                                    labels = c("Arrival of Europeans", "Colonial Period", "Independence Era"),
                                    include.lowest = TRUE)

        ggplot(filtered_data, aes(x = year, y = category, label = event, color = period)) +
            geom_point(size = 4) +
            geom_text(vjust = 2, angle = 45, hjust = 1, size = 4) +
            scale_x_continuous(breaks = filtered_data$year) +
            scale_color_manual(values = c("red", "black", "blue")) +
            theme_minimal() +
            labs(title = "Key Events in Solomon Islands' History", x = "Year", y = "Category") +
            theme(axis.text.y = element_blank(),
                  plot.title = element_text(hjust = 0.5),
                  panel.background = element_rect(fill = "lightblue"),
                  panel.grid.major = element_line(color = "white"),
                  panel.grid.minor = element_line(color = "white"),
                  legend.position = "bottom")
    })
}

# Run the application
shinyApp(ui = ui, server = server)

```

Then I show some key features for the solomon islands.Data(<https://en.wikipedia.org/wiki/Solomon_Islands>)

Description:The Solomon Islands, located in the southwestern Pacific Ocean, is an archipelago nation comprising six major islands and over 900 smaller ones. It's part of Melanesia in Oceania, northeast of Australia. The islands have a rich history, first settled around 30,000 BC. They gained independence from the United Kingdom in 1978. The capital, Honiara, is on Guadalcanal, the largest island. The Solomon Islands are known for their diverse cultures, languages, and a vibrant ecosystem, including rainforests and coral reefs.

# Key demographics

```{r echo=FALSE}
solomon_islands_data <- data.frame(
  Number = 1:9,
  Province = c("Central Province", "Choiseul Province", "Guadalcanal Province", "Isabel Province", "Makira-Ulawa Province", "Malaita Province", "Rennell and Bellona Province", "Temotu Province", "Western Province"),
  Capital = c("Tulagi", "Taro Island", "Honiara", "Buala", "Kirakira", "Auki", "Tigoa", "Lata", "Gizo"),
  Premier = c("Stanely Manetiva", "Harrison Benjamin", "Anthony Veke", "Lesley Kikolo", "Julian Maka'a", "Martin Fini", "Japhet Tuhanuku", "Clay Forau", "David Gina"),
  Area = c(615, 3837, 5336, 4136, 3188, 4225, 671, 895, 5475),
  Population_1999 = c(21577, 20008, 60275, 20421, 31006, 122620, 2377, 18912, 62739),
  Population_per_km2_2009 = c(42.4, 6.9, 17.5, 6.3, 12.7, 32.6, 4.5, 23.9, 14.0),
  Population_2009 = c(26051, 26371, 93613, 26158, 40419, 137596, 3041, 21362, 76649),
  Population_2022 = c(33476, 38453, 166838, 36688, 57396, 163085, 4465, 25701, 102083)
)

ui <- fluidPage(
  DTOutput("solomon_table")
)

server <- function(input, output) {
  output$solomon_table <- renderDT({
    datatable(solomon_islands_data, options = list(
      autoWidth = TRUE,
      columnDefs = list(list(width = '200px', targets = "_all"))
    ))
  })
}

shinyApp(ui = ui, server = server)

```

```{r echo=FALSE,warning=FALSE}
solomon_islands_data <- data.frame(
  Number = 1:9,
  Province = c("Central Province", "Choiseul Province", "Guadalcanal Province", "Isabel Province", "Makira-Ulawa Province", "Malaita Province", "Rennell and Bellona Province", "Temotu Province", "Western Province"),
  Capital = c("Tulagi", "Taro Island", "Honiara", "Buala", "Kirakira", "Auki", "Tigoa", "Lata", "Gizo"),
  Premier = c("Stanely Manetiva", "Harrison Benjamin", "Anthony Veke", "Lesley Kikolo", "Julian Maka'a", "Martin Fini", "Japhet Tuhanuku", "Clay Forau", "David Gina"),
  Area = c(615, 3837, 5336, 4136, 3188, 4225, 671, 895, 5475),
  Population_1999 = c(21577, 20008, 60275, 20421, 31006, 122620, 2377, 18912, 62739),
  Population_per_km2_2009 = c(42.4, 6.9, 17.5, 6.3, 12.7, 32.6, 4.5, 23.9, 14.0),
  Population_2009 = c(26051, 26371, 93613, 26158, 40419, 137596, 3041, 21362, 76649),
  Population_2022 = c(33476, 38453, 166838, 36688, 57396, 163085, 4465, 25701, 102083)
)
ui <- fluidPage(
  titlePanel("Population of Solomon Islands Provinces"),
  selectInput("year", "Select Year", choices = c("1999", "2009", "2022")),
  plotOutput("populationPlot")
)


server <- function(input, output) {
  output$populationPlot <- renderPlot({
    year_col <- paste0("Population_", input$year)
    data_to_plot <- solomon_islands_data %>%
      select(Province, Population = all_of(year_col))
ggplot(data_to_plot, aes(x = Province, y = Population, fill = Province)) +
  geom_bar(stat = "identity", color = "black", size = 0.5) +  
  theme_minimal(base_size = 14) +  # Uses a minimal theme with larger base font size
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12, face = "bold"), # Bolder, larger x-axis labels
    axis.text.y = element_text(size = 12, face = "bold"), # Bolder y-axis labels
    axis.title = element_text(size =  14, face = "bold"), # Bolder axis titles
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5) # Bolder and centered plot title
  ) +
  labs(y = "Population", x = "Province", title = paste("Population of Solomon Islands Provinces in", input$year)) +
  scale_fill_brewer(palette = "Paired")  

  })
}

shinyApp(ui = ui, server = server)
```

We can see from the Solomon Islands that the population of key provinces has increased significantly in both periods, 1999-2009, 2009-2022.

```{r echo=FALSE}
data <- data.frame(
  Category = rep(c("Geography", "Culture", "History", "Economy", "Demographics"), each = 5),
  Island = c(rep(c("Solomon Islands", "Fiji", "Vanuatu", "Papua New Guinea", "New Caledonia"), 5)),
Information = c(
  # Geography
  "Six major islands and over 900 smaller ones, volcanic mountain ranges, dense rainforests, lagoons",
  "More than 330 islands, rugged landscapes, palm-lined beaches, coral reefs",
  "About 82 volcanic islands",
  "Eastern half of New Guinea, dense rainforests, active volcanoes",
  "French territory, numerous islands, palm-lined beaches, rich marine life",
  # Culture
  "Diverse ethnic groups, wood carvings, music, dance",
  "Multicultural, indigenous Fijian, Indo-Fijian, Pacific Islander cultures",
  "Strong Melanesian culture, land diving rituals",
  "Hundreds of ethnic groups and languages",
  "Mix of French and Melanesian cultures, Kanak traditions",
  # History
  "Influenced by European exploration, colonialism, and World War II",
  "Former British colony until 1970",
  "Anglo-French condominium until 1980",
  "Independent from Australia since 1975",
  "French territory, with ongoing independence discussions",
  # Economy
  "Based on agriculture, forestry, fishing, and mining",
  "Diversified economy with tourism, sugar, and garment industries",
  "Agricultural economy with significant tourism",
  "Rich in natural resources, with an economy centered on mining",
  "Large economy supported by nickel mining and French financial aid",
  # Demographics
  "Predominantly Melanesian, with Polynesian and Micronesian communities",
  "Majority indigenous Fijians and Indo-Fijians",
  "Primarily Ni-Vanuatu (Melanesian)",
  "Over 800 languages spoken",
  "Majority Kanak (indigenous Melanesians), with Europeans, Polynesians, and Southeast Asians"
)
)
ui <- fluidPage(
  titlePanel("Comparative Analysis of Melanesian Islands"),
  sidebarLayout(
    sidebarPanel(
      selectInput("category", "Select Category:", choices = c("Geography", "Culture", "History", "Economy", "Demographics"))
    ),
    mainPanel(
      tableOutput("infoTable")
    )
  )
)

# Define server logic
server <- function(input, output) {
  output$infoTable <- renderTable({
    # Filter data based on the selected category
    filteredData <- data %>% filter(Category == input$category)
    return(filteredData)
  })
}

# Run the application 
shinyApp(ui = ui, server = server)
```
```{r echo=FALSE,warning=FALSE}

gdp_data <- read.csv("GDP.csv")
gdp_long <- melt(gdp_data, id.vars = "Country.Name", variable.name = "Year", value.name = "GDP")
gdp_long$Year <- as.numeric(gdp_long$Year)+1969

ui <- fluidPage(
  titlePanel("Per capita GDP of Solomon Islands VS Papua New Guinea "),
  sidebarLayout(
    sidebarPanel(
      sliderInput("yearRange",
                  "Select Year Range:",
                  min = min(gdp_long$Year),
                  max = max(gdp_long$Year),
                  value = c(min(gdp_long$Year), max(gdp_long$Year)+1969),
                  step = 1,
                  ticks = TRUE,  # Add ticks to the slider
                  animate = TRUE  # Optional: add animation for the slider
      )
    ),
    mainPanel(
      plotOutput("gdpPlot")
    )
  )
)

server <- function(input, output) {
  output$gdpPlot <- renderPlot({
    filtered_data <- subset(gdp_long, Year >= input$yearRange[1] & Year <= input$yearRange[2])
    ggplot(filtered_data, aes(x = Year, y = GDP, group = Country.Name, color = Country.Name)) +
      geom_line() +
      geom_point() +  
      scale_color_brewer(palette = "Set1") +  
      theme_minimal() +
      labs(title = "GDP Over Time", x = "Year", y = "GDP (USD)") +
      scale_y_continuous(labels = scales::dollar)  
  })
}

shinyApp(ui, server)



```

I make a table about the five differences between the  Melanesian Islands,and I also make a plot for Per capita GDP of Solomon Islands VS Papua New Guinea,for the table part,there has specific illustration of the data,so I don't make explaination.

For the plot,General Trend: Both countries show an overall increasing trend in GDP from 1970 to around 2020, indicating economic growth over this 50-year period.

Volatility: There are periods of volatility where the GDP fluctuates more significantly, such as around 1990 for Papua New Guinea and the early 2000s for both countries. This could be due to external economic shocks, changes in government policies, commodity price fluctuations (particularly if their economies are dependent on a few key exports), or other socio-economic factors.

Growth Rates: While both countries follow a generally similar pattern, there are times when their growth rates diverge. For instance, between 2000 and 2010, the Solomon Islands' GDP appears to grow at a steadier rate compared to Papua New Guinea, which experiences more pronounced ups and downs.

Recent Trends: In the most recent years shown on the chart (around 2020), there's a sharp downturn for both countries, possibly reflecting the impact of the COVID-19 pandemic on their economies.

Comparison: Throughout the entire time period, Papua New Guinea's GDP remains higher than that of the Solomon Islands. However, the gap in GDP between the two countries seems to narrow as time progresses, especially during the period from 2000 to 2020.

# SWOT analysis
```{r echo=FALSE}


# Create data for each SWOT category
swot_data <- list(
  Strengths = data.frame(
    Aspect = c("Natural Resources", "Biodiversity", "Cultural Heritage", "Agricultural Potential", "Renewable Energy Resources"),
    Description = c(
      "Rich in natural resources, including forests, minerals, and fisheries, which can be leveraged for economic growth.",
      "High biodiversity with potential for eco-tourism and conservation projects.",
      "Strong cultural heritage and diversity can be attractive to tourists.",
      "Fertile land that is suitable for various types of agriculture.",
      "Potential for the development of renewable energy sources like hydro, solar, and wind."
    )
  ),
  Weaknesses = data.frame(
    Aspect = c("Geographic Dispersion", "Economic Dependency", "Limited Industrial Base", "Infrastructure Deficits", "Challenges in Public Services"),
    Description = c(
      "The country consists of many islands, which makes infrastructure development and governance challenging.",
      "Heavy reliance on a few key sectors, such as logging and fisheries, makes the economy vulnerable to shocks.",
      "Lack of diversification in industry can limit economic opportunities and resilience.",
      "Inadequate infrastructure in terms of transportation, utilities, and communication.",
      "Education, healthcare, and other public services may be underdeveloped, affecting human capital development."
    )
  ),
  Opportunities = data.frame(
    Aspect = c("Tourism Development", "Foreign Investment", "Trade Partnerships", "Sustainable Practices", "Regional Cooperation"),
    Description = c(
      "Potential to expand the tourism industry, especially eco-tourism and cultural tourism.",
      "Attracting foreign direct investment for resource development and infrastructure.",
      "Forming trade partnerships with other nations to expand market access for Solomon Islands products.",
      "Opportunity to develop sustainable fishing and logging practices.",
      "Engaging in regional cooperation for economic development and stability."
    )
  ),
  Threats = data.frame(
    Aspect = c("Climate Change", "Over-reliance on Imports", "Political Instability", "Global Market Fluctuations", "Environmental Degradation"),
    Description = c(
      "Vulnerability to climate change and natural disasters, which can disrupt the economy and livelihoods.",
      "Dependence on imported goods for many basic necessities can be problematic if supply chains are disrupted.",
      "Risk of political instability that can deter investment and development.",
      "Prices for key export commodities can be volatile on the global market.",
      "Unsustainable exploitation of natural resources could lead to long-term environmental damage."
    )
  )
)

# Define UI
ui <- fluidPage(
  titlePanel("SWOT Analysis of Solomon Islands"),
  tabsetPanel(
    tabPanel("Strengths", DTOutput("strengthsTable")),
    tabPanel("Weaknesses", DTOutput("weaknessesTable")),
    tabPanel("Opportunities", DTOutput("opportunitiesTable")),
    tabPanel("Threats", DTOutput("threatsTable"))
  )
)

# Define server logic
server <- function(input, output) {
  output$strengthsTable <- renderDataTable({datatable(swot_data$Strengths)})
  output$weaknessesTable <- renderDataTable({datatable(swot_data$Weaknesses)})
  output$opportunitiesTable <- renderDataTable({datatable(swot_data$Opportunities)})
  output$threatsTable <- renderDataTable({datatable(swot_data$Threats)})
}

# Run the app
shinyApp(ui, server)

```

